Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-07-01 JCB/conclusion_JCB.tex

\TODOJerome{Etoffer la conclusion}
In this article we presented a new and efficient way of exploring the mutational landscape of an RNA under structural constraints,
and apply our techniques to identify and fix sequencing errors. In addition, we introduced a new scoring scheme to measure the
likelihood of sequencing errors that combines the classical nearest-neighbour energy model parameters \cite{Turner2010} to the
recently introduced isostericity matrices \cite{Stombaugh2009}. The latter accounting for geometrical discrepancies occurring
during base pair replacements.

>>>>

%\TODOJerome{Etoffer la conclusion}
In this article we presented a new and efficient way of exploring the mutational landscape of an RNA under structural constraints,
and apply our techniques to identify and fix sequencing errors. In addition, we introduced a new scoring scheme to measure the
likelihood of sequencing errors that combines the classical nearest-neighbour energy model parameters \cite{Turner2010} to the
recently introduced isostericity matrices \cite{Stombaugh2009}. The latter accounting for geometrical discrepancies occurring
during base pair replacements.
